\documentclass{amsart}
\usepackage{amsmath,amssymb,latexsym,color,ulem,mathabx,pdflscape,bbm}
\usepackage{geometry}
\usepackage{tikz}
\usepackage[bookmarks=true, bookmarksopen=true, bookmarksdepth=3,bookmarksopenlevel=2, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, menucolor=blue, urlcolor=blue]{hyperref}
\usepackage{cancel}

\usepackage[draft]{say}
\newcommand{\sayNR}[1]{\say[NR]{\color{purple}\;#1}}
\newcommand{\sayDR}[1]{\say[DR]{\color{red}\;#1}}
\newcommand{\saySS}[1]{\say[SS]{\color{blue}\;#1}}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}{Question}

\numberwithin{theorem}{section}

\newcommand{\bfb}{{\boldsymbol{b}}}
\newcommand{\bfc}{{\boldsymbol{c}}}
\newcommand{\bfd}{{\boldsymbol{d}}}
\newcommand{\bfe}{{\boldsymbol{e}}}
\newcommand{\bfg}{{\boldsymbol{g}}}
\newcommand{\bfk}{{\boldsymbol{k}}}
\newcommand{\bfl}{{\boldsymbol{\ell}}}
\newcommand{\bfn}{{\boldsymbol{n}}}
\newcommand{\bfr}{{\boldsymbol{r}}}
\newcommand{\bfu}{{\boldsymbol{u}}}
\newcommand{\bfx}{{\boldsymbol{x}}}
\newcommand{\bfy}{{\boldsymbol{y}}}

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\cR}{\mathcal{R}}

\newcommand{\fd}{\mathfrak{d}}
\newcommand{\fp}{\mathfrak{p}}

\newcommand{\CC}{\mathbb{C}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\TT}{\mathbb{T}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\bOne}{\mathbbm{1}}

\newcommand{\ol}[1]{{\overline{#1}}}
\newcommand{\vv}[1]{{{}^\vee \! #1}}

\newcommand{\Aut}{\operatorname{Aut}}
\newcommand{\beps}{{\boldsymbol{\varepsilon}}}
\newcommand{\eps}{{\varepsilon}}
\newcommand{\Col}{\operatorname{Col}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\dpt}{\operatorname{dp}}
\newcommand{\hgt}{\operatorname{ht}}
\newcommand{\Id}{\operatorname{Id}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\obeta}{{\overline{\beta}}}
\newcommand{\oi}{{\overline{\imath}}}
\newcommand{\ot}{{\overline{t}}}
\newcommand{\rep}{\mathrm{rep}}
\newcommand{\sgn}{{\operatorname{sgn}}}
\newcommand{\Span}{{\operatorname{Span}}}
\newcommand{\WA}{{W\!\!A}}
\newcommand{\wt}{{\operatorname{wt}}}

\title{Dominance Regions for Affine Cluster Algebras}

\author{Nathan Reading}
\author{Dylan Rupel}
\author{Salvatore Stella}

\begin{document}
  \begin{abstract}
    We study the dominance order for $\bfg$-vectors in affine cluster algebras.
  \end{abstract}
  \maketitle

  Let $\lambda$ be an imaginary $\bfg$-vector.
  \begin{enumerate}
    \item What is the condition that determines whether the separating hyperplane for a mutation map cuts between two imaginary domains of linearity?
    \item The intersection of $P_\lambda$ with each cone corresponding to an imaginary cluster is convex.
      Indeed, for any seed $t$, consider the mutation of that cone along the sequence $\bfk$ corresponding to $t$.
      Intersecting this cone with $\eta^{\widetilde B^{t_+}}_\bfk(\lambda)+\widetilde B^t \RR_{\ge0}^n$ produces a convex region which mutates back to a convex region under $\left(\eta^{\widetilde B^{t_+}}_\bfk\right)^{-1}$.
    \item $\lambda$ does not dominate $c^r\lambda$ for any $r\in\ZZ$ unless $c^r\lambda=\lambda$.
      Indeed, if there existed an $r$ so that $\lambda$ dominates $c^r\lambda$ for all imaginary $\lambda$, then by repeatedly applying $c^r$ we would see that $c^r\lambda$ also dominates $\lambda$ which is impossible unless $\lambda=c^r\lambda$.
    \item For $\lambda\in\RR^m$ and sequences $\bfk=(k_N,\ldots,k_1)$ of mutations from $t_+$ to $t$, define 
      \[
        \cP^{t_+}_\lambda = \bigcap_\bfk \left(\eta^{\widetilde B^{t_+}}_\bfk\right)^{-1}\big(\left\{\eta^{\widetilde B^{t_+}}_\bfk(\lambda)+\widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\big).
      \]
      Then for any sequence $\bfl$ joining $t_+$ to $t'_+$, we have $\eta^{\widetilde B^{t_+}}_\bfl \cP^{t_+}_\lambda=\cP^{t'_+}_{\lambda'}$ where $\lambda'=\eta^{\widetilde B^{t_+}}_\bfl(\lambda)$.
  \end{enumerate}

  For $j\ge 1$, we have $(\eta_{c^j}^{\widetilde B})^{-1}\left(\{\eta_{c^j}^{\widetilde B}(\lambda)+\mu_{c^j}\widetilde B \alpha\}\right) = \{\lambda - \widetilde B C_{c^{j+1}} \alpha \}$ and $(\eta_{c^{-j}}^{\widetilde B})^{-1}\left(\{\eta_{c^{-j}}^{\widetilde B}(\lambda)+\mu_{c^{-j}}\widetilde B \alpha\}\right) = \{\lambda + \widetilde B C_{c^{-j}} \alpha \}$ for $\lambda$ sufficiently near $\fd_\infty$.

  \saySS{define imaginary, real, and the imaginary cone $\cI$, $\widetilde B^+$, $\delta$}
  \begin{theorem}
    \label{thm:main}
    Given $\lambda \in \RR^m$, let $z\ge 0$ be the minimum value such that $\lambda+z\widetilde B^+\delta$ is real.
    \saySS{We need to say why such an $z$ exists, i.e. $-\widetilde B^+\delta$ positively spans the imaginary ray.}
    Then the dominance region $\cP_\lambda$ is the line segment $\{\lambda+x\widetilde B^+\delta:0\le x\le z\}$.
  \end{theorem}

  The uniform formulation of Theorem~\ref{thm:main} hides in itself two cases: if $\lambda$ is real then $z=0$ and $\cP_\lambda$ is just the point $\lambda$; otherwise $z>0$ and $\cP_\lambda$ is a proper line segment.
  The former case was already established in \cite{qin} in complete generality; we will reprove it here by elementary means as a corollary of a result needed in the proof of the latter case.
  The proof of Theorem~\ref{thm:main} is divided into several intermediate claims; we begin by showing that, for imaginary $\lambda$, $\cP_\lambda \subseteq \cI$.

  \begin{lemma}
    \label{lemma:P in I}
    If $\lambda$ is imaginary, then $\cP_\lambda\subseteq \cI$.
  \end{lemma}
  \begin{proof}
    By definition, $\cP_\lambda$ is contained in $\{\lambda + \widetilde B^+ \alpha : \alpha \in  \RR_{\ge0}^n\}$ which is a proper cone since $\widetilde B^+$ is full rank.
    In particular, for sufficiently large $z$, the dominance region $\cP_\lambda$ does not intersect the half space $H = \{ \lambda' : \langle -B^+\delta, \lambda' \rangle \ge z \}$.
    \saySS{Think about how to write this better.}
    Suppose by contradiction that there exists some point $\lambda' \in \cP_\lambda\setminus\, \cI$.
    Since $\cP_\lambda$ is stable under mutations $\eta_{\bfk}^{\widetilde B^+}(\lambda')\in \cP_\lambda$ for any sequence of indices $\bfk$.
    \saySS{WARNING: do this only for sequences fixing $\lambda$.}
    \saySS{Define mutation maps. of course we already knew this was to be done!}
    Moreover, since $\lambda'$ is not in $\cI$, for sufficiently large $r$ the sequence $\bfk = (n,\dots,1)^r$ satisfies $\eta_{\bfk}^{\widetilde B^+}(\lambda')\in H$ contradicting our previous observation.
    \saySS{We need to say much more about this: explain finite/infinite c-orbits and how limits work.}
  \end{proof}

For $j\in\ZZ$, let $\langle j\rangle$ be the element of $[1,n]$ congruent to $j$ mod $n$.
If $j>0$ let $\bfk_j$ be the sequence $(\langle j \rangle, \langle j-1 \rangle,\dots,\langle 1\rangle)$; it has length $j$.
Let $\bfk_0$ denote the empty sequence.
If $j<0$ let $\bfk_j$ be the sequence $(\langle j+1 \rangle, \langle j+2 \rangle, \dots, \langle 0 \rangle)$; it has length $-j$.

Denote by $t_j$ the seed obtained from $t_0$ mutating along the sequence $\bfk_j$.
\begin{remark}
  \label{rk:seed to sorting}
  If $j \geq 0$ the seed $t_j$ corresponds to the $c$-sorting element whose $c$-sorting word is the prefix of $c^{\infty}$ of length $j$.
  If $j\leq -n$ the seed $t_j$ corresponds to the $c^{-1}$-sorting element whose $c^{-1}$-sorting word is the prefix of  $c^{-\infty}$ of length $n-j$.
\end{remark}
Set $\cP_{\lambda,j}= \left(\eta^{\widetilde B^{t_0}}_{\bfk_j}\right)^{-1}\left(\left\{\eta^{\widetilde B^{t_0}}_{\bfk_j}(\lambda)+ \widetilde B^{t_j}\alpha:\alpha\in\RR^n_{\ge0}\right\}\right)$; then $\cP_\lambda\subseteq \bigcap_{j\in\ZZ} \cP_{\lambda,j}$.

\begin{lemma}
  \label{lemma:Pj positive}
  For any $j\geq 0$, there exists a full-dimensional subset $L_j$ of $\RR^m$ such that $\cI \subseteq L_j$ and, for any $\lambda\in\cI$,
  \[
    \cP_{\lambda,j}\cap L_j = \left\{\lambda + \widetilde B^{t_0} C^{t_j}\alpha:\alpha\in\RR^n_{\ge0}\right\} \cap L_j.
  \]
\end{lemma}
\begin{proof}
  First observe that the $\langle i+1\rangle$-st coordinate of $\eta^{\widetilde B^{t_0}}_{\bfk_i}(\lambda)$ is non-positive for every $i\in\ZZ$.
  Indeed, since $\eta^{\widetilde B^{t_0}}_{\bfk_i}(\lambda)\in \mu_{\bfk_i}(\cI)$, it is of the form $M v$ for some non-negative vector $v$ and some matrix $M$ whose $\langle i+1\rangle$-st row is a negative  elementary unit vector ($M$ is the matrix of the change of coordinates in between positive $\bfd$-vectors and non-initial $\bfg$-vectors).
  \saySS{I am trying very hard not to mention the Euler matrix here nor source-sink moves if possible}
  In particular $\eta^{\widetilde B^{t_0}}_{\bfk_j}$ acts on $\cI$ as $\widetilde E^{t_{j-1}}_{\langle j \rangle,-} \cdots \widetilde E^{t_0}_{1,-}$

  Let $L_j$ be the maximal cone on which $\eta^{\widetilde B^{t_0}}_{\bfk_j}$ and $\widetilde E^{t_{j-1}}_{\langle j \rangle,-} \cdots \widetilde E^{t_0}_{1,-}$ agree. 
  \saySS{Should we something to explain why this is not just $\cI$?}
  We compute
  \begin{align*}
    \cP_{\lambda,j}\cap L_j 
    & = \left(\eta^{\widetilde B^{t_0}}_{\bfk_j}\right)^{-1}\left(\left\{\eta^{\widetilde B^{t_0}}_{\bfk_j}(\lambda)+ \widetilde B^{t_j}\alpha:\alpha\in\RR^n_{\ge0}\right\}\right) \cap L_j \\
    & = \left(\widetilde E^{t_{j-1}}_{\langle j \rangle,-} \cdots \widetilde E^{t_0}_{1,-}\right)^{-1}\left(\left\{\widetilde E^{t_{j-1}}_{\langle j \rangle,-} \cdots \widetilde E^{t_0}_{1,-}(\lambda)+ \mu_{\bfk_j}(\widetilde B^{t_0})\alpha:\alpha\in\RR^n_{\ge0}\right\}\right) \cap L_j \\
    & = \left\{\lambda + \widetilde E^{t_0}_{1,-} \cdots \widetilde E^{t_{j-1}}_{\langle j \rangle,-}\mu_{\bfk_j}(\widetilde B^{t_0})\alpha:\alpha\in\RR^n_{\ge0}\right\} \cap L_j \\
    & = \left\{\lambda + \widetilde B^{t_0} F^{t_0}_{1,-} \cdots F^{t_{j-1}}_{\langle j \rangle,-}\alpha:\alpha\in\RR^n_{\ge0}\right\} \cap L_j \\
    & = \left\{\lambda + \widetilde B^{t_0} C^{t_j}\alpha:\alpha\in\RR^n_{\ge0}\right\} \cap L_j
  \end{align*}
  where the last identity follows from Lemma~\ref{le:c-matrix factorization} and the observation that the $\langle i+1\rangle$-st $\bfc$-vector in the seed $t_i$ is positive (it is the leftmost skip for the corresponding $c$-sorting word).
\end{proof}

\begin{lemma}
  \label{lemma:Pj negative}
  For any $j\leq 0$, there exists a full-dimensional subset $L_j$ of $\RR^m$ such that $\cI \subseteq L_j$ and, for any $\lambda\in\cI$,
  \[
    \cP_{\lambda,j}\cap L_j = \left\{\lambda - \widetilde B^{t_0} C^{t_{j-n}}\alpha:\alpha\in\RR^n_{\ge0}\right\} \cap L_j.
  \]
\end{lemma}
\begin{proof}
  The proof of this lemma follows closely the proof of the previous one with some important distinctions.

  For any $i\in\ZZ$ the $\langle i \rangle$-th coordinate of $\eta^{\widetilde B^{t_0}}_{\bfk_i}(\lambda)$ is non-negative. 
  Indeed since $\lambda$ and $-\frac{1}{2}\widetilde B^{t_0}\delta$ belong to the same maximal cone, the $\langle i\rangle$-th coordinates of $\eta^{\widetilde B^{t_0}}_{\bfk_i}(\lambda)$ and $\eta^{\widetilde B^{t_0}}_{\bfk_i}(-\frac{1}{2}\widetilde B^{t_0}\delta)=-\frac{1}{2}\widetilde B^{t_i}\delta$ weekly agree in sign.
  But the $\langle i \rangle$-th row of $\widetilde B^{t_i}$ contains only non-positive integers  while $\delta$ is a vector of positive integers and the claim follows.
  \saySS{Maybe we should use this argument also in the other proposition to avoid talking about the Euler matrix.}
  In particular $\eta^{\widetilde B^{t_0}}_{\bfk_j}$ acts on $\cI$ as $\widetilde E^{t_{j+1}}_{\langle j+1 \rangle,+} \cdots \widetilde E^{t_0}_{n,+}$.
  Let $L_j$ be the maximal cone on which $\eta^{\widetilde B^{t_0}}_{\bfk_j}$ and $\widetilde E^{t_{j+1}}_{\langle j+1 \rangle,+} \cdots \widetilde E^{t_0}_{n,+}$ agree.
  As before we compute 
  \begin{align*}
    \cP_{\lambda,j}\cap L_j 
    & = \left(\eta^{\widetilde B^{t_0}}_{\bfk_j}\right)^{-1}\left(\left\{\eta^{\widetilde B^{t_0}}_{\bfk_j}(\lambda)+ \widetilde B^{t_j}\alpha:\alpha\in\RR^n_{\ge0}\right\}\right) \cap L_j \\
    & = \left(\widetilde E^{t_{j+1}}_{\langle j+1 \rangle,+} \cdots \widetilde E^{t_0}_{n,+}\right)^{-1}\left(\left\{\widetilde E^{t_{j+1}}_{\langle j+1 \rangle,+} \cdots \widetilde E^{t_0}_{n,+}(\lambda)+ \mu_{\bfk_j}(\widetilde B^{t_0})\alpha:\alpha\in\RR^n_{\ge0}\right\}\right) \cap L_j \\
    & = \left\{\lambda + \widetilde E^{t_{j+1}}_{\langle j+1 \rangle,+} \cdots \widetilde E^{t_0}_{n,+}\mu_{\bfk_j}(\widetilde B^{t_+})\alpha:\alpha\in\RR^n_{\ge0}\right\} \cap L_j \\
    & = \left\{\lambda + \widetilde B^{t_0} F^{t_{j+1}}_{\langle j+1 \rangle,+} \cdots F^{t_0}_{n,+}\alpha:\alpha\in\RR^n_{\ge0}\right\} \cap L_j.
  \end{align*}
  Now observe that the first $n$ $\bfc$-vectors encountered while mutating along $\bfk_j$ are positive while the remaining ones are negative.
  (Provided that $j<-n$, otherwise they are all positive.)
  Note also that $F^{t_{1-n}}_{1,-} \cdots F^{t_0}_{n,-}=-1$ and that $F^{t_{i}}_{\langle i \rangle,\varepsilon} = F^{t_{i-n}}_{\langle i-n \rangle,\varepsilon}$ for any $i$ and $\varepsilon$.
  We get
  \[
    F^{t_{j+1}}_{\langle j+1 \rangle,+} \cdots F^{t_0}_{n,+}
    =
    F^{t_{j-n+1}}_{\langle j-n+1 \rangle,+} \cdots F^{t_-n}_{n,+} 
    =
    - F^{t_{j-n+1}}_{\langle j-n+1 \rangle,+} \cdots F^{t_{-n}}_{n,+} F^{t_{1-n}}_{1,-} \cdots F^{t_0}_{n,-}
    =
    - C^{t_{j-n}}
  \]
  again by Lemma~\ref{le:c-matrix factorization} and we are done.
\end{proof}
\saySS{Note to self: if $\lambda$ is a cluster monomial in $t$ then exactly the same argument shows that $\cP_{\lambda,j}\cap K_t$ has the same expression. This should imply that $\cP_\lambda\cap K_t$ is just the point $\lambda$ but it is not enough to conclude that $\cP_\lambda=\lambda$ because we do not know that $\cP_\lambda$ is connected.}

  \begin{proposition}
    \label{prop:ray upperbound}
    Let $\lambda$ be imaginary with $z$ minimal such that $\lambda+z\widetilde B^{t_0}\delta$ is real.
    Then $\cP_\lambda$ is contained in the half line $\{\lambda+x\widetilde B^{t_0}\delta: x\le z\}$.
  \end{proposition}
  \begin{proof}
    Since $\cP_\lambda\subseteq \bigcap_{j\in\ZZ}\cP_{\lambda,nj}$ it suffices to show that $\bigcap_{j\in\ZZ}\cP_{\lambda,nj}$ is a half line.
    Moreover, since by Lemma~\ref{lemma:P in I} $\cP_\lambda\subseteq \cI$, it suffices to show that $\bigcap_{j\in\ZZ}\left(\cP_{\lambda,nj}\cap L_j\right)$ is a half line.
    In view of Lemmas~\ref{lemma:Pj positive}~and~\ref{lemma:Pj negative}, since $\widetilde B^{t_0}$ has full rank, it sufficies to show that 
    \[
      \bigcap_{j\in\ZZ}\left\{(-1)^{\sgn(j)} C^{t_{nj}}\alpha:\alpha\in\RR^n_{\ge0}\right\}
    \]
    is the line spanned by $\delta$.

    By Remark~\ref{rk:seed to sorting}, if $j\geq 0$ the $i$-th column of $C^{t_{nj}}$ is the root $c^j \alpha_i$.
    Similarly, if $j\leq -1$ the $i$-th column of $-C^{t_j}$ is the root $c^{j+1} \alpha_i$.
    AAARGHHH This screws everything up, we cant use it to show that if $c^j\alpha_i$ is in a finite orbit then there is a $j'<0$ such that $-c^j\alpha_i\in -C^{t_{nj'}}$!!!!!!
  \end{proof}
 
  From now on the superscipt $t$ will mean that object to which it is applied is expressed in terms of the seed $t$.
  Whenever $t=t_+$ and there is no ambiguity we will drop the superscript.
  We will also drop the superscript when the reference seed is irrelevant.

  Let $\lambda$ be a $\bfg$-vector in the interior of $\cI$ and let $t$ be any seed adjacent to the imaginary cluster containing $\lambda$ i.e. suppose that the cluster expansion of $\lambda$ is $\sum_{i=1}^{n-2} a_i \xi_i -a_0 B_{t_0} \delta$ (with $\xi_i$ in a finite $c$-orbit,  $a_i\geq 0$ for all $i\geq 1$, and $a_0>0$) and that the $\bfg$-vectors at $t$ are $\{\xi_1,\dots,\xi_n\}$.
  We now describe the exchange matrix at $t$.
  
  First observe that, $\{\xi_i\}_{i\in[1,n-2]}$ are $\bfg$-vectors in finite $c$-orbits and $\{\xi_{n-1},\xi_n\}$ are $\bfg$-vectors in infinite orbits.
  Since $\lambda$ is in the interior of $\cI$ the set $\{\xi_i\}_{i\in[1,n-2]}$ must contain at least one $\bfg$-vector from the top layer in each tube and if a tube has size $\ell$ then it must contain precisely $\ell-1$ $\bfg$-vectors from it. 
  Since $\bfg$-vectors from the top layer of a tube are incompatible with one another, the set $\{\xi_i\}_{i\in[1,n-2]}$ must contain exactly one $\bfg$-vector from the top layer in each tube.
  Let $p_i+1$ be the size of the $i$-th tube (so that $p_1+p_2+p_3 = n-2$).
  To fix ideas we assume that $0\leq p_1\leq p_2 \leq p_3$.
  Up to relabelling we can assume that each subset $\{\xi_1,\dots,\xi_{p_1}\}$, $\{\xi_{p_1+1},\dots,\xi_{p_1+p_2}\}$, and $\{\xi_{p_1+p_2+1},\dots,\xi_{p_1+p_2+p_3}\}$ consists of $\bfg$-vectors from the same tube and that $\xi_{p_1}$, $\xi_{p_1+p_2}$, and $\xi_{p_1+p_2+p_3}$ are the $\bfg$-vectors in the top layer of each. 
  We will therefore consider the decomposition of the exchange matrix at $t$ in blocks $B_{ij}$ given by the partition $(p_1,p_2,p_3,2)\vdash n$.

  We claim that the block $B_{ii}$ is an exchange matrix of type $A_{p_i}$ for all $i\in[1,2,3]$.
  Indeed observe first that any tube is of type $A$ (c.f. \cite{afforb}[Proposition 4.4 (2)]) hence the corresponding symmetrizer is constant so that $B_{ii}$ is symmetric.
  Moreover the (coefficient-free) exchange relations for $j< n-2$, $i\neq p_1,p_1+p_2$ are of the form
  \begin{equation}
    \label{eq:tube_rels}
    x_{\xi_j} x_\zeta = x_{\xi_j+\zeta} + x_{\xi_j\uplus\zeta}
  \end{equation}
  for some $\zeta$ the $\bfg$-vector of a cluster variable, and $\xi_j\uplus\zeta$ (the symmetric difference of $\xi_j$ and $\zeta$\saySS{The standard notation for symmetric difference would have been $\Delta$ but it is definitely an overloaded symbol. I decided to follow CFZ's notation for the finite type case of which this is an instance I guess}) the $\bfg$-vector of a cluster monoimial, both in the same tube where $\xi_j$ lives.
  Finally, the exchange relations among those listed in (\ref{eq:tube_rels}) that are supported on the $i$-th tube coincide with those in a cluster algebra of finite type $A_{p_i}$ in which one cluster variable has been frozen (the bijection being given by the identification of the $\bfd$-vectors with respect to the simples at the base of the tube with the $\bfd$-vectors with respect to the fan triangulation of a $(p_i+3)$-gon).
  Our claim follows.

  Equation (\ref{eq:tube_rels}) together with sign-skew-symmetry also imply that the blocks $B_{ij}$ with $i\neq j\in[1,2,3]$ can only have a non-zero entry in the bottom right corner.
  
  Similarly blocks $B_{i4}$ for $i\in[1,2,3]$  can only be non-zero in the last row and blocks $B_{4j}$ for $j\in[1,2,3]$  can only be non-zero in the last column.
  Since the exchanges of $\xi_{p_1}$, $\xi_{p_1+p_2}$, and $\xi_{p_1+p_2+p_3}$ are not imaginary each of these matrices has at least one non-zero entry.
  
  Next we claim that $B_{44}$, up to a possible relabelling, is of the form
    \[
      \left[
      \begin{array}{cc} 
        0 & a \\ 
        -b & 0 \\
      \end{array}
      \right]
    \] 
  with $a>0$, $b>0$ and $ab=4$.
  This follows from the observation that the subalgebra generated by the cluster variables in all seeds containig $\{x_{\xi_i}\}_{i\in[1,n-2]}$ is an affine cluster algebra of rank 2.
  Indeed let $\ell$ be the minimum positive power such that $c^\ell$ fixes pointwise $\cI$.
  Then the collection 
  \[
    \left\{x_{c^{j\ell} \xi_i}\right\}_{j\in\ZZ,i\in[1,n]}
  \]
  is infinite (because both $\xi_{n-1}$ and $\xi_n$ are in infinite $c$-orbits) and it is contained in the subalgebra which thus contains infinitely many cluster variables. 
  Since it is a subalgebra of an affine type cluster algebra it is also affine and our claim follows.

  For each $i\in[p_1,p_1+p_2,p_1+p_2+p_3]$ consider now the submatrix of the exchange matrix at $t$ consisting of the rows and columns $i,n-1,n$.
  As its $2\times 2$ submatrix on rows and columns $n-1$ and $n$ is affine all of its non-diagonal entries must be non-zero.
  Otherwise it would be an exchange matrix of wild type.
  By direct inspection we see that the only possibilities are then those in Table~\ref{tab:possible_submatrices}.
	Note that, as the sign patterns are the same regardless of the chosen tube mutating in directions $n-1$ and $n$ do not affect the exchange matrix at $t$ outside of rows and columns $n-1$ and $t$.
	Moreover, by direct inspection, it is easy to see that these two mutations only change the signs in both the last two columns and the last two rows.

  Some further considerations on the root lengths, together with \cite{affdenom}[Table 1], show that submatrices of types $A_{4}^{(2)}$, $G_{2}^{(1)}$, and $D_{4}^{(3)}$ can only appear in cases having a single tube so that the exchange matrix at $t$ is completely determined in these cases.
  It remains to consider the possibly non-zero entries in the matrices $B_{ij}$ with $i\neq j\in[1,2,3]$.
  By taking the $4\times 4$ submatrix consisting of the rows and columns corresponding to indices of the $\bfg$-vectors in the top layer of the $i$-th and $j$-th tube together with $n-1$ and $n$ we see directly that a non-zero entry in $B_{ij}$ would produce a cluster algebra of wild type.

	\begin{table}
	\caption{Possible submatrices}
	\label{tab:possible_submatrices}	
	\begin{center}
	\begin{tabular}{|ll|ll|ll|}
	Type & matrix & Type & matrix \\
	\hline & & & \\[-1ex]
	$A_{2}^{(1)}$ & $\left[\begin{array}{rrr}
	0 & 1 & -1 \\
	-1 & 0 & 2 \\
	1 & -2 & 0
	\end{array}\right]$ & & \\[4ex]
	$C_{2}^{(1)}$ & $\left[\begin{array}{rrr}
	0 & 2 & -2 \\
	-1 & 0 & 2 \\
	1 & -2 & 0
	\end{array}\right]$ &
	$D_{3}^{(2)}$ & $\left[\begin{array}{rrr}
	0 & 1 & -1 \\
	-2 & 0 & 2 \\
	2 & -2 & 0
	\end{array}\right]$ \\[4ex]
	$G_2^{(1)}$ & $\left[\begin{array}{rrr}
	0 & 3 & -3 \\
	-1 & 0 & 2 \\
	1 & -2 & 0
	\end{array}\right]$ &
	$D_4^{(3)}$ & $\left[\begin{array}{rrr}
	0 & 1 & -1 \\
	-3 & 0 & 2 \\
	3 & -2 & 0
	\end{array}\right]$ \\[4ex]
	$A_{4}^{(2)}$ & $\left[\begin{array}{rrr}
	0 & 1 & -2 \\
	-2 & 0 & 4 \\
	1 & -1 & 0
	\end{array}\right]$ &
	$A_{4}^{(2)}$ & $\left[\begin{array}{rrr}
	0 & 2 & -1 \\
	-1 & 0 & 1 \\
	2 & -4 & 0
	\end{array}\right]$ 
	\end{tabular}
	\end{center}	
	\end{table}

  To summarize, the exchange matrix at $t$, after relabelling, is of the form
    \[
      \left[
      \begin{array}{cccc} 
        B_{11} & 0 & 0 & B_{14} \\ 
        0 & B_{22} & 0 & B_{24} \\
        0 & 0 & B_{33} & B_{34} \\
        B_{41} & B_{42} & B_{43} & B_{44}
      \end{array}
      \right]
    \] 
    with $B_{11}, B_{22}, B_{33}$ of finite type $A$, $B_{i4}$ non zero only in the last row, $B_{4j}$ non zero only in the last column, and such that the non-zero rows and columns in 
    \[
      \left[
      \begin{array}{cc} 
        0 & B_{i4} \\ 
        B_{4i} & B_{44}
      \end{array}
      \right]
    \] 
    form one of the matrices from Table~\ref{tab:possible_submatrices}.


  Using Proposition~\ref{prop:ray upperbound}, the fact that $\cP_\lambda\subseteq \{\lambda + \widetilde B^+ \alpha : \alpha \in  \RR_{\ge0}^n\}$, and the fact that $\widetilde B^+$ is full rank, we deduce immediately the following upper bound for $\cP_\lambda$.
  \begin{corollary}
    \label{cor:upperbound}
    Let $\lambda$ be imaginary with $z$ minimal such that $\lambda+z\widetilde B^+\delta$ is real.
    Then $\cP_\lambda$ is contained in the line segment $\{\lambda+x\widetilde B^+\delta: 0\le x\le z\}$
  \end{corollary}


  \begin{lemma}
    \label{le:coxeter power}
    There exists $r>0$ so that $c^{-p} s_n \ldots s_{\ell+1} \alpha_\ell$ has full support for any $p\ge r$ and any $\ell$.
  \end{lemma}
  \begin{proof}
    By \cite[Theorem 1.2(1)]{Reading-Stella} and \cite[Section 1]{Dlab-Ringel}, the set $\{c^q s_n \ldots s_{\ell+1} \alpha_\ell:q\in\ZZ\}$ is infinite.
    On the other hand, there are only finitely many roots without full support.
  \end{proof}

  Suppose $t$ is a seed corresponding to a $c$-sortable element $v$.
  The construction of Cambrian frameworks in \cite{Combinatorial_frameworks_for_cluster_algebras} \sayDR{after Prop 5.4} provides the following description of the columns of $C^t$.
  Let $s_{a_1}\dots s_{a_N}$ be the $c$-sorting word of $v$. 
  For an index $i$ consider the longest prefix $s_{a_1} \dots s_{a_p}$ of $s_{a_1}\dots s_{a_N}$ such that any instance of $s_i$ in the corresponding prefix of $c^\infty$ is also in $s_{a_1} \dots s_{a_p}$.
  Then the $i$-th column of $C^t$ is the root $s_{a_1} \dots s_{a_p}\alpha_i$.
  This root is positive if and only if the word $s_{a_1} \dots s_{a_p} s_i$ is reduced.

  This description of $C^t$ is instrumental in proving the next two results.

 
  \begin{proposition}
    \label{prop:no postinjectives}
    Let $t$ be a seed corresponding to a $c$-sortable element $v$\saySS{Explain this correspondence} whose $c$-sorting word starts with $c^r$ for $r$ as in Lemma~\ref{le:coxeter power}.
    Then the columns of $C^t$ are not roots of the form $\pm c^{-p} s_n \ldots s_{\ell+1} \alpha_\ell$ with $p\ge 0$.
  \end{proposition}
  \begin{proof}
    Let $k$ be the index such that $s_k$ is the leftmost reflection of $c^\infty$ omitted in $s_{a_1}\dots s_{a_N}$.
    Since \saySS{do we need a reference for this?}  $c^p$ is reduced for any $p$, the $k$-th column of $C^t$ is a positive root of the form $c^q s_1 \cdots s_{k-1} \alpha_k$ and, following \cite[Theorem 1.2(1)]{Reading-Stella} and \cite[Section 1]{Dlab-Ringel}, it is not of the form $c^{-p} s_n \ldots s_{\ell+1} \alpha_\ell$ for $p\ge0$. 

    All the other columns of $C^t$ will be roots of the form  $c^q s_{b_1} \cdots s_{b_{i-1}} \alpha_{b_i}$ for $q\ge r$ with $k\ne b_j$ for any $j$.
    Suppose that one such root were also of the form $\pm c^{-p} s_n \ldots s_{\ell+1} \alpha_\ell$ for $p\ge0$ and some index $\ell$.
    Then $\pm c^{-p-q} s_n \ldots s_{\ell+1} \alpha_\ell=s_{b_1} \cdots s_{b_{i-1}} \alpha_{b_i}$ would be a root without full support.
    But $p+q\ge r$, contradicting Lemma~\ref{le:coxeter power}.
  \end{proof}

  \begin{proposition}
    Let $t$ be the seed associated to $c^r$ for $r$ as in Lemma~\ref{le:coxeter power}. 
    Then $C^t$ contains at least one column of the form $c^q s_1 \cdots s_{k-1} \alpha_k$ and at least one column of the form $-c^q s_1 \cdots s_{k-1} \alpha_k$.
    The remaining columns that are not of the form $\pm c^q s_1 \cdots s_{k-1} \alpha_k$ lie in finite $c$-orbits.
  \end{proposition}
  \begin{proof}
    The first column of $C^t$ is $c^r \alpha_1$ and the last column of $C^t$ is $c^r\alpha_n=-c^{r-1} s_1\cdots s_{n-1} \alpha_n$.
    By Proposition~\ref{prop:no postinjectives}, any column of $C^t$ which is not of the form $\pm c^q s_1 \cdots s_{k-1} \alpha_k$ must lie in a finite $c$-orbit.
  \end{proof}

  For $t\in\TT_n$, define $K^t:=\{G_t\alpha:\alpha\in\RR_{\ge0}^n\}$.
  For $\lambda \in \widetilde K^t := K^t \times \RR^{m-n}$, set 
  \[L^t_{\lambda,\pm}:=\{\lambda \pm \widetilde B^{t_+} C^t\alpha:\alpha\in\RR_{\ge0}^n\}.\]
  \begin{lemma}
    For $\lambda\in \widetilde K^t$, we have $\cP_\lambda\cap \widetilde K^t\subseteq L^t_{\lambda,+}\cap L^t_{\lambda,-}$.
  \end{lemma}
  \begin{proof}
    Suppose $t$ is obtained from $t^+$ by mutating along the sequence $\bfk^+=(k_N,\ldots,k_1)$.
    Let $\bfl$ denote a red-to-green sequence for $B^t$, it exists following \cite[Corollary 3.2.2]{muller} since $B^{t_+}$ is acyclic and hence has a maximal green sequence.
    Write  $\bfk^-$ for the concatenation of $\bfl$ and $\bfk^+$.

    First observe that $\left(\eta^{\widetilde B^{t_+}}_{\bfk^+}\right)^{-1}$ acts linearly on $\RR_{\ge0}^n\times \RR^{m-n}$.
    Then, since $\left(\eta^{\widetilde B^{t_+}}_{\bfk^+}\right)^{-1}=\eta^{\widetilde B^t}_{(\bfk^+)^{op}}$, we see from \cite[Equation (1.13)]{nakanishi-zelevinsky} that the action on $\RR_{\ge0}^n\times \RR^{m-n}$ is given by the matrix $\widetilde G^t$, i.e. 
    \[\left(\eta^{\widetilde B^{t_+}}_{\bfk^+}\right)^{-1}(\RR_{\ge0}^n\times \RR^{m-n})=\widetilde G^t(\RR_{\ge0}^n\times \RR^{m-n})=\widetilde K^t.\]
    By Lemma~\ref{le:mutation maps}, we have $\left(\eta^{\widetilde B^{t_+}}_{\bfk^-}\right)^{-1}=\left(\eta^{\widetilde B^{t_+}}_{\bfk^+}\right)^{-1}\left(\eta^{\widetilde B^t}_\bfl\right)^{-1}$.
    But $\eta^{\widetilde B^t}_\bfl(\RR_{\ge0}^n\times \RR^{m-n})=(\RR_{\le0}^n\times \RR^{m-n})$ and so $\left(\eta^{\widetilde B^{t_+}}_{\bfk^-}\right)^{-1}(\RR_{\le0}^n\times \RR^{m-n})=-\widetilde G^t(\RR_{\le0}^n\times \RR^{m-n})=\widetilde K^t$.

    It follows that
    \begin{align*}
      S_{\bfk^+,\lambda}\cap \widetilde K^t
      &= \left(\eta^{\widetilde B^{t_+}}_{\bfk^+}\right)^{-1}\left\{\eta^{\widetilde B^{t_+}}_{\bfk^+}(\lambda)+\widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \widetilde K^t\\
      &= \left(\eta^{\widetilde B^{t_+}}_{\bfk^+}\right)^{-1}\left(\left\{\eta^{\widetilde B^{t_+}}_{\bfk^+}(\lambda)+\widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \big( \RR_{\ge0}^n\times \RR^{m-n}\big)\right)\\
      &= \widetilde G^t \left(\left\{\eta^{\widetilde B^{t_+}}_{\bfk^+}(\lambda)+\widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \big( \RR_{\ge0}^n\times \RR^{m-n}\big)\right)\\
      &= \left\{\lambda+\widetilde G^t \widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \widetilde K^t\\
      &= \left\{\lambda+\widetilde B^{t_+} C^t \alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \widetilde K^t\\
      &\subseteq L^t_{\lambda,+},
    \end{align*}
    where the last equality uses Corollary~\ref{cor:GB=BC}.
    Similarly, we have
    \begin{align*}
      S_{\bfk^-,\lambda}\cap \widetilde K^t
      &= \left(\eta^{\widetilde B^{t_+}}_{\bfk^-}\right)^{-1}\left\{\big(\eta^{\widetilde B^{t_+}}_{\bfk^-}(\lambda)+\widetilde B^t\alpha\big):\alpha\in\RR^n_{\ge0}\right\}\cap \widetilde K^t\\
      &= \left(\eta^{\widetilde B^{t_+}}_{\bfk^-}\right)^{-1}\left(\left\{\eta^{\widetilde B^{t_+}}_{\bfk^-}(\lambda)+\widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \big( \RR_{\le0}^n\times \RR^{m-n}\big)\right)\\
      &= -\widetilde G^t \left(\left\{\eta^{\widetilde B^{t_+}}_{\bfk^-}(\lambda)+\widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \big( \RR_{\le0}^n\times \RR^{m-n}\big)\right)\\
      &= \left\{\lambda-\widetilde G^t \widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \widetilde K^t\\
      &= \left\{\lambda-\widetilde B^{t_+} C^t \alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \widetilde K^t\\
      &\subseteq L^t_{\lambda,-}.
    \end{align*}
    Since $\cP_\lambda\subseteq S_{\bfk^\pm,\lambda}$, the claim follows.
  \end{proof}

  \begin{lemma}
    \label{le:euler pairing}
    For any root $\beta$ the product $(\beta^\vee)^T B^+ \delta$ is
    \begin{itemize}
      \item positive if $\beta = c^p s_1\dots s_{k-1}\alpha_k$ for some $p\in\ZZ$ and some $k$,
      \item negative if $\beta = c^{-p} s_n\dots s_{k+1}\alpha_k$ for some $p\in\ZZ$ and some $k$,
      \item zero otherwise.
    \end{itemize}
  \end{lemma}

  \begin{proof}
    Begin by observing that the product $(\beta^\vee)^T B^+ \gamma$ is invariant under source-sink moves.
    Indeed, $(s_1\beta^\vee)^T B^+ (s_1\gamma) = (\beta^\vee)^T (E^{t_+}_{1,-} B^+ F^{t_+}_{1,-}) \gamma = (\beta^\vee)^T \mu_1(B^+) \gamma$ and similarly for $s_n$.

    Using this invariance, it suffices to establish the first claim for $p=0$ and $k=1$.
    Since $\delta$ is in the kernel of $A$, we have that $(\alpha_1^\vee)^T B^+ \delta$ = $(\alpha_1^\vee)^T (A+B^+) \delta$.
    The result then follows immediately from the observation that $A + B^+$ is a lower-triangular matrix with positive entries on the diagonal and that $\delta$ has full support.

    Similarly it suffices to establish the second claim only for $p=1$ and $k=1$.
    By the same computation we just did we have $(-\alpha_1^\vee)^T B^+ \delta$ = $-(\alpha_1^\vee)^T (A+B^+) \delta <0$.

    For the remaining case, since $B^+$ is skew-symmetrizable, $(\delta^\vee)^T B^+ \delta = 0$.
    By assumption, the root $\beta$ is in a finite $c$-orbit (c.f. \cite[Proposition 1.9 and Section 1, final Remark]{Dlab-Ringel}) so that there is a positive $\ell$ such that $\sum_{i=0}^\ell c^i \beta = q \delta$ for some $q\neq 0$ (cf. \cite{afforb}).
    By the invariance under source-sink moves we have that $(c\beta^\vee)^T B^+ \delta = (\beta^\vee)^T B^+ \delta$ and we can compute
    \[
      0 = q\, (\delta^\vee)^T B^+ \delta = \left(\sum_{i=0}^\ell c^i \beta^\vee\right)^T B^+ \delta = \ell\, (\beta^\vee)^T B^+ \delta
    \]
  to conclude that $(\beta^\vee)^T B^+ \delta = 0$.
  \end{proof}

  \begin{lemma}
    \label{le:imaginary direction mutation}
    Suppose $t$ is obtained from $t_+$ by mutating along the sequence $\bfk=(k_N,\ldots,k_1)$ passing through the seeds $t_+=t_1,\ldots,t_{N+1}=t$.
    Consider seeds $t'_1,\ldots,t'_{N+1}$ with $t'_{i+1}$ obtained from $t'_i$ by mutation in direction $k_i$ and $t'_1$ obtained from $t_+$ by mutating along the sequence $(n,\ldots,1)$ sufficiently many times that $\big(G^{\vee,t'_i}\big)^T \delta$ is a nonnegative vector for every $i$. 
    \saySS{i.e. on the positive side of $\delta^\perp$. This sentence needs to be justified; somewhere we need to discuss the plane $\delta^\perp$ and how it cuts the g-ector fan.}
    \sayDR{Think about $\vee$ or no $\vee$ in the $G$ matrix here.}
    
    For $1\le i\le N$, let $\varepsilon_i$ be the opposite of the sign of the $k_i$-th column of $C^{\vee,t'_i}$.
    Set $\delta_1=\delta$ and define $\delta_{i+1} = F^{t_i}_{k_i,\varepsilon_i} \cdots F^{t_1}_{k_1,\varepsilon_1} \delta$.
    Then the following hold.
    \begin{enumerate}
      \item $\delta_i$ is a nonnegative vector for $1\le i\le N+1$;
      \item For $1\le i\le N$, if the $k_i$-th entry of $-\widetilde B^{t_i} \delta_i$ is nonzero then its sign is $\varepsilon_i$.
      \item $\eta_\bfk^{\widetilde B^+}\left(-\widetilde B^+\delta\right)=-\widetilde B^t \delta_{N+1}$.
    \end{enumerate}
  \end{lemma}
  \begin{remark}
    Something about $\big(G^{\vee,t'_i}\big)^T \delta$ being the absolute value of the kernel of the quasi-Cartan companion $A^{t_N}$.
    Maybe mention something about companion bases not existing in affine types.
  \end{remark}
  \begin{proof}
    First observe that $F^{t_i}_{k_i,\varepsilon_i}=F^{t'_i}_{k_i,\varepsilon_i}$ for each $i$.
    By Lemma~\ref{le:factorize dual matrices}, $F^{t'_i}_{k_i,\varepsilon_i} \cdots F^{t'_1}_{k_1,\varepsilon_1}=(G^{\vee,t'_{i+1}})^T M$ for some matrix $M$ such that $M\delta=\delta$ since $t'_1$ is obtained from $t_+$ by repeatedly mutating along the sequence $(n,\ldots,1)$.
    Therefore $\delta_i = (G^{\vee,t'_i})^T \delta$ is a nonnegative vector by assumption.
    
    The first $n$ entries of $\widetilde B^{t_i} \delta_i$ coincide with the entries of $B^{t_i} \delta_i$.
    We apply Corollary~\ref{cor:dual BG=CB} to get
    \[
      B^{t_i} \delta_i 
      = B^{t'_i} \delta_i 
      = B^{t'_i} (G^{\vee,t'_i})^T \delta
      = \big(C^{\vee,t'_i}\big)^T B^+ \delta.
    \]
    Redefining the seeds $t_i'$, if needed, to ensure that the hypotheses of Proposition~\ref{prop:no postinjectives} are satisfied and combining Lemma~\ref{le:euler pairing} with Lemma~\ref{prop:no postinjectives} we see that the $k_i$-th sign of $\widetilde B^{t_i} \delta_i$ weakly agrees with the sign of the $k_i$-th column of $C^{\vee,t'_i}$.

    To conclude, we are now able to compute 
    \begin{align*}
      \eta_\bfk^{\widetilde B^+}\left(-\widetilde B^+\delta\right)
      &= - \widetilde E^{t_N}_{k_N,\varepsilon_N} \cdots \widetilde E^{t_1}_{k_1,\varepsilon_1} \widetilde B^+ \delta\\
      &= - \widetilde B^t F^{t_N}_{k_N,\varepsilon_N} \cdots F^{t_1}_{k_1,\varepsilon_1} \delta\\
      &= - \widetilde B^t \delta_{N+1}.
    \end{align*}
  \end{proof}

  \begin{corollary}
    Suppose $t$ is obtained from $t_+$ by mutating along the sequence $\bfk=(k_N,\ldots,k_1)$ passing through the seeds $t_+=t_1,\ldots,t_{N+1}=t$.
    Then the imaginary cone at $t_{N+1}$ is contained in the hyperplane orthogonal to $\widetilde \delta_{N+1}$.
  \end{corollary}
  \begin{proof}
    We work by induction on $N$, the claim being known for $N=0$.
    Recall that $\cI^{t_N}$
    \saySS{This should be defined}
    \saySS{do we want to change notation: $\fd_\infty$ instead of $\cI$?}
    is cut into (finitely many) domains of linearity for the mutation maps and that $-B^{t_N}\delta_N$ is contained in each of them.
    Therefore the $k_N$-th coordinate of any $\lambda\in\cI^{t_N}$ weekly agrees in sign with the $k_N$-th coordinate of $-B^{t_N}\delta_N$.

    If the $k_N$-th entry of $-B^{t_N}\delta_N$ is nonzero it must have sign $\varepsilon_N$, then for any $\lambda\in\cI^{t_N}$ we have  $\eta_{k_N}^{\widetilde B^{t_N}}(\lambda) = \widetilde E^{t_N}_{k_N,\varepsilon_N} \lambda$ and we compute
    \begin{align*}
      \langle \widetilde \delta_{N+1}, \eta_{k_N}^{\widetilde B^{t_N}}(\lambda) \rangle 
      & =
      \langle \widetilde F_{k_N,\varepsilon_N}^{t_N} \widetilde \delta_N, \widetilde E^{t_N}_{k_N,\varepsilon_N} \lambda \rangle\\
      & =
      \left(  \widetilde F_{k_N,\varepsilon_N}^{t_N} \widetilde \delta_N \right) ^T \widetilde D \widetilde E^{t_N}_{k_N,\varepsilon_N} \lambda \\
      & =
      \widetilde \delta_N^T \left( \widetilde F_{k_N,\varepsilon_N}^{t_N} \right) ^T \widetilde D \widetilde E^{t_N}_{k_N,\varepsilon_N} \lambda \\
      & =
      \widetilde \delta_N^T \widetilde D \widetilde E^{t_N}_{k_N,\varepsilon_N} \widetilde E^{t_N}_{k_N,\varepsilon_N} \lambda \\
      & =
      \widetilde \delta_N^T \widetilde D \lambda \\
      & =
      \langle \widetilde \delta_N, \lambda \rangle \\
      &=
      0
    \end{align*}
    where we used the definition of pairing and the fact that, for any $t$, $k$, and $\varepsilon$,  $\left(\widetilde F_{k,\varepsilon}^t \right) ^T \widetilde D = \widetilde D \widetilde E^t_{k,\varepsilon}$.
    \saySS{Note to self: The symmetrized $D$ is there because the dual basis to weights is coroots}

    If instead the $k_N$-th entry of $-B^{t_N}\delta_N$ is zero then $\widetilde F_{k_N,+}^{t_N}\widetilde \delta_N=\widetilde \delta_{N+1}=\widetilde F_{k_N,-}^{t_N}\widetilde\delta_N$ since the $k_N$-th row of $-B^{t_N}$ is equal to the $k_N$-th row of $F_{k_N,+}^{t_N}-F_{k_N,-}^{t_N}$.
    For $\lambda\in\cI^{t_N}$ let $\varepsilon$ the sign such that $\eta_{k_N}^{\widetilde B^{t_N}}(\lambda) = \widetilde E^{t_N}_{k_N,\varepsilon} \lambda$ and compute as before
    \[
      \langle \widetilde \delta_{N+1}, \eta_{k_N}^{\widetilde B^{t_N}}(\lambda) \rangle 
      =
      \langle \widetilde F_{k_N,\varepsilon}^{t_N} \widetilde \delta_N, \widetilde E^{t_N}_{k_N,\varepsilon} \lambda \rangle
      =
      \langle \widetilde \delta_N, \widetilde E_{k_N,\varepsilon}^{t_N} \widetilde E^{t_N}_{k_N,\varepsilon} \lambda \rangle
      =
      \langle \widetilde \delta_N, \lambda \rangle
      =
      0.
    \]
  \end{proof}

  \begin{proposition}
    Let $\lambda$ be imaginary with $z$ minimal such that $\lambda+z\widetilde B^+\delta$ is real.
    Then $\cP_\lambda$ contains the line segment $\{\lambda+x\widetilde B^+\delta:0\le x\le z\}$.
  \end{proposition}
  \begin{proof}
    Suppose $t$ is obtained from $t_+$ by mutating along the sequence $\bfk$.
    To establish the claim we need to show that, for $0\le x\le z$, 
    \[
      \eta_{\bfk}^{\widetilde B^+}(\lambda + x\widetilde B^+\delta) 
      \in
      \left\{\eta_{\bfk}^{\widetilde B^+}(\lambda) + \widetilde B^{t}\alpha : \alpha\in  \RR^n_{\ge 0}\right\}.
    \]
    Since the vectors $\lambda$, $\lambda + x\widetilde B^+\delta$, and $-\widetilde B^+\delta$ all live in the same cone of the mutation fan, \saySS{we need to decide which presentation we will use and quote afftheta} we have that
    \[
      \eta_{\bfk}^{\widetilde B^+}(\lambda + x\widetilde B^+\delta)
      =
      \eta_{\bfk}^{\widetilde B^+}(\lambda) -x \eta_{\bfk}^{\widetilde B^+}(-\widetilde B^+\delta)
    \]
    and our task reduces to showing that 
    \[
      \eta_{\bfk}^{\widetilde B^+}(-\widetilde B^+\delta)
      = 
      -\widetilde B^{t}\alpha
    \]
    for some positive vector $\alpha\in\RR^n_{\ge 0}$.
    Lemma~\ref{le:imaginary direction mutation} gives an explicit formula for such a vector $\alpha$ and completes the proof.
  \end{proof}

  This concludes the proof of Theorem~\ref{thm:main}.
$ $ 

\hrule

$ $
Some old stuff we no longer need

  For $t\in\TT_n$, define $K^t:=\{G_t\alpha:\alpha\in\RR_{\ge0}^n\}$.
  For $\lambda \in \widetilde K^t := K^t \times \RR^{m-n}$, set 
  \[L^t_{\lambda,\pm}:=\{\lambda \pm \widetilde B^{t_+} C^t\alpha:\alpha\in\RR_{\ge0}^n\}.\]
  \begin{lemma}
    For $\lambda\in \widetilde K^t$, we have $\cP_\lambda\cap \widetilde K^t\subseteq L^t_{\lambda,+}\cap L^t_{\lambda,-}$.
  \end{lemma}
  \begin{proof}
    Suppose $t$ is obtained from $t^+$ by mutating along the sequence $\bfk^+=(k_N,\ldots,k_1)$.
    Set $\bfk^-=(n,\ldots,1,k_N,\ldots,k_1)$.

    First observe that $\left(\eta^{\widetilde B^{t_+}}_{\bfk^+}\right)^{-1}$ acts linearly on $\RR_{\ge0}^n\times \RR^{m-n}$.
    Then, since $\left(\eta^{\widetilde B^{t_+}}_{\bfk^+}\right)^{-1}=\eta^{\widetilde B^t}_{(\bfk^+)^{op}}$, we see from \cite[Equation (1.13)]{nakanishi-zelevinsky} that the action on $\RR_{\ge0}^n\times \RR^{m-n}$ is given by the matrix $\widetilde G^t$, i.e. 
    \[\left(\eta^{\widetilde B^{t_+}}_{\bfk^+}\right)^{-1}(\RR_{\ge0}^n\times \RR^{m-n})=\widetilde G^t(\RR_{\ge0}^n\times \RR^{m-n})=\widetilde K^t.\]
    By Lemma~\ref{le:mutation maps}, we have $\left(\eta^{\widetilde B^{t_+}}_{\bfk^-}\right)^{-1}=\left(\eta^{\widetilde B^{t_+}}_{\bfk^+}\right)^{-1}\left(\eta^{\widetilde B^t}_{(n,\cdots,1)}\right)^{-1}$.
    But $\eta^{\widetilde B^t}_{(n,\cdots,1)}(\RR_{\ge0}^n\times \RR^{m-n})\stackrel{?}{=}(\RR_{\le0}^n\times \RR^{m-n})$ and so $\left(\eta^{\widetilde B^{t_+}}_{\bfk^-}\right)^{-1}(\RR_{\le0}^n\times \RR^{m-n})=-\widetilde G^t(\RR_{\le0}^n\times \RR^{m-n})=\widetilde K^t$.

    It follows that
    \begin{align*}
      S_{\bfk^+,\lambda}\cap \widetilde K^t
      &= \left(\eta^{\widetilde B^{t_+}}_{\bfk^+}\right)^{-1}\left\{\eta^{\widetilde B^{t_+}}_{\bfk^+}(\lambda)+\widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \widetilde K^t\\
      &= \left(\eta^{\widetilde B^{t_+}}_{\bfk^+}\right)^{-1}\left(\left\{\eta^{\widetilde B^{t_+}}_{\bfk^+}(\lambda)+\widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \big( \RR_{\ge0}^n\times \RR^{m-n}\big)\right)\\
      &= \widetilde G^t \left(\left\{\eta^{\widetilde B^{t_+}}_{\bfk^+}(\lambda)+\widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \big( \RR_{\ge0}^n\times \RR^{m-n}\big)\right)\\
      &= \left\{\lambda+\widetilde G^t \widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \widetilde K^t\\
      &= \left\{\lambda+\widetilde B^{t_+} C^t \alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \widetilde K^t\\
      &\subseteq L^t_{\lambda,+},
    \end{align*}
    where the last equality uses Corollary~\ref{cor:GB=BC}.
    Similarly, we have
    \begin{align*}
      S_{\bfk^-,\lambda}\cap \widetilde K^t
      &= \left(\eta^{\widetilde B^{t_+}}_{\bfk^-}\right)^{-1}\left\{\big(\eta^{\widetilde B^{t_+}}_{\bfk^-}(\lambda)+\widetilde B^t\alpha\big):\alpha\in\RR^n_{\ge0}\right\}\cap \widetilde K^t\\
      &= \left(\eta^{\widetilde B^{t_+}}_{\bfk^-}\right)^{-1}\left(\left\{\eta^{\widetilde B^{t_+}}_{\bfk^-}(\lambda)+\widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \big( \RR_{\le0}^n\times \RR^{m-n}\big)\right)\\
      &= -\widetilde G^t \left(\left\{\eta^{\widetilde B^{t_+}}_{\bfk^-}(\lambda)+\widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \big( \RR_{\le0}^n\times \RR^{m-n}\big)\right)\\
      &= \left\{\lambda-\widetilde G^t \widetilde B^t\alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \widetilde K^t\\
      &= \left\{\lambda-\widetilde B^{t_+} C^t \alpha:\alpha\in\RR^n_{\ge0}\right\}\cap \widetilde K^t\\
      &\subseteq L^t_{\lambda,-}.
    \end{align*}
    Since $\cP_\lambda\subseteq S_{\bfk^\pm,\lambda}$, the claim follows.
  \end{proof}

Below here is the stuff we wrote so far.

  %%%%%%%%%%%%%%%%%%%%%%
  \section{Introduction}
  Cluster algebras are recursively defined commutative rings.
  Since their discovery by Fomin and Zelevinsky through an intensive study of dual canonical bases \cite{...}, cluster algebras have found application throughout mathematics, including Lie theory \cite{...}, representation theory \cite{...}, Teichm\"uller theory \cite{...}, and mathematical physics \cite{...}.
  See \cite{...} for a more exhaustive description of the deep connections found to cluster algebras.

  A guiding question in the theory has always been to understand possible bases of a cluster algebra.
  Qin put bounds on how the pointed bases can be related.
  


  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \section{Mutation Maps and Dominance}
  Fix $m\ge n$.
  Let $\widetilde B=(b_{ij})$ be an $m\times n$ exchange matrix with principal $n\times n$ submatrix $B$.
  Note that our exchange matrices are tall, which matches the convention of \cite{qin}.
  Then $B$ is skew-symmetrizable with $DB$ skew-symmetric for some diagonal integer matrix $D=\diag(d_1,\ldots,d_n)$.
 
  For $b\in\RR$, write $[b]_+=\max(b,0)$.
  %Similarly, given a vector $\bfb\in\RR^m$, let $[\bfb]_+$ denote the vector in $\RR_{\ge0}^n$ obtained by applying $[-]_+$ to each entry.
  Given a sign $\varepsilon\in\{\pm\}$ and $1\le k\le n$, define an $m\times m$ matrix $\widetilde E_{k,\varepsilon}=(e_{ij})$ with
  \begin{equation}
    \label{e:left mutation matrix}
    e_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ [\varepsilon b_{ik}]_+ & \text{if $i\ne j=k$;}\\ 0 & \text{otherwise;} \end{cases}
  \end{equation}
  and an $n\times n$ matrix $F_{k,\varepsilon}=(f_{ij})$ with
  \begin{equation}
    \label{eq:right mutation matrix}
    f_{ij}=\begin{cases} 1 & \text{if $k\ne i=j$;}\\ -1 & \text{if $k=i=j$;}\\ [-\varepsilon b_{kj}]_+ & \text{if $k=i\ne j$;}\\ 0 & \text{otherwise.} \end{cases}
  \end{equation}
  Observe that $\widetilde E^2_{k,\varepsilon}=\bOne_m$ and $F^2_{k,\varepsilon}=\bOne_n$ for any choice of $\varepsilon$.
  Then define $\mu_k\widetilde B=\widetilde E_{k,\varepsilon} \widetilde B F_{k,\varepsilon}$.
  Using the identity $b_{ij}=[b_{ij}]_+-[-b_{ij}]_+$ it is easy to see that $\mu_k\widetilde B$ doesn't depend on the choice of sign $\varepsilon$.
  Moreover, the principal part $\mu_k B$ of $\mu_k\widetilde B$ is again skew-symmetrizable using the same matrix $D$.

  Given a matrix $M$, denote by $M_{\bullet k}$ (resp. $M_{k \bullet}$) the $k$-th column (resp. $k$-th row) of $M$ and write $[M]_{\bullet k}$ (resp $[M]_{k\bullet}$)  the square matrix whose $k$-th column (resp. $k$-th row) matches that of $M$ with all other entries being zero.
  \begin{lemma}
    For $\varepsilon\in\{\pm1\}$ and $1\le k \le n$, we have 
    \begin{enumerate}
      \item $\widetilde E_{k,-\varepsilon} \widetilde E_{k,\varepsilon} = \bOne_m + \varepsilon [\widetilde B]_{\bullet k}$, $\widetilde E_{k,\varepsilon} - \widetilde E_{k,-\varepsilon} = \varepsilon [\widetilde B]_{\bullet k}$, and $\widetilde E_{k,\varepsilon} [\widetilde B]_{\bullet k} = [\widetilde B]_{\bullet k}$;
      \item $F_{k,-\varepsilon} F_{k,\varepsilon} = \bOne_n + \varepsilon [B]_{k \bullet}$, $F_{k,\varepsilon} - F_{k,-\varepsilon} = -\varepsilon [B]_{k \bullet}$, and $F_{k,\varepsilon} [B]_{k \bullet} = -[B]_{k \bullet}$.
    \end{enumerate}
  \end{lemma}
  \begin{proof}
    This is immediate from the equality $\varepsilon b_{ij}=[\varepsilon b_{ij}]_+-[-\varepsilon b_{ij}]_+$.
  \end{proof}

  To record sequences of these matrix mutations, we introduce the $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and edges labeled by $\{1,\ldots,n\}$.
  Associate $m\times n$ matrices $\widetilde{B}^t$ with principal part $B^t$ to the vertices $t\in\TT_n$ so that:
  \begin{itemize}
    \item $\widetilde{B}^{t_0}=\widetilde{B}$;
    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $\widetilde{B}^{t'}=\mu_k \widetilde{B}^t$.
  \end{itemize}
  Given a sequence $\bfk=(k_N,\ldots,k_1)$ with $k_i\in\{1,\ldots,n\}$ write $\mu_\bfk$ for the iterated matrix mutation $\mu_{k_N}\circ\cdots\circ\mu_{k_1}$.
  Then more directly, when $t'$ is obtained from $t$ by following edges labeled by $\bfk=(k_N,\ldots,k_1)$, we have $\widetilde B^{t'}=\mu_\bfk \widetilde B$.

  A skew-symmetric matrix $B=(b_{ij})$ is \emph{acyclic} if there is no sequence $i_1,\ldots,i_r,i_{r+1}=i_1$ so that $b_{i_\ell i_{\ell+1}}>0$ for $1\le\ell\le r$.
  In the case when $B$ is acyclic, there exists a permutation $\sigma$ of $\{1,\ldots,n\}$ so that $r<r'$ implies $b_{\sigma_r \sigma_{r'}}\ge 0$.
  We also associate to $B$ a Cartan matrix $A=(a_{ij})$ with $a_{ii}=2$ and $a_{ij}=-|b_{ij}|$i for $i\ne j$.
  We say that the mutation pattern is of \emph{affine type} if there exists acyclic $B^t$ whose associated Cartan matrix gives rise to an affine Dynkin diagram.
  
  Assume there exists $t_+\in\TT_n$ so that $B^{t_+}=(b^{t_+}_{ij})$ is acyclic with $b^{t_+}_{ij}\ge 0$ for $i<j$.
  This provides a Coxeter element $c=s_1\cdots s_n$ in the Weyl group associated to $A$.
  
  Given $\bfk=(k_N,\ldots,k_1)$ and any $\widetilde B$, define the piecewise-linear \emph{mutation map} $\eta^{\widetilde B}_\bfk:\RR^m\to\RR^m$ where $\eta^{\widetilde B}_\bfk(\nu)$ is the last column of $\mu_\bfk([\widetilde{B}\;\nu])$.
  \begin{lemma}\mbox{}
    \label{le:mutation maps}
    \begin{enumerate}
      \item $\left(\eta^{\widetilde{B}}_\bfk\right)^{-1}=\eta^{\mu_\bfk\widetilde{B}}_{\bfk^{op}}$, where $\bfk^{op}:=(k_1,\ldots,k_N)$.
      \item Consider a sequence of mutations $\bfk=\bfk''\bfk'$ where $\mu_{\bfk'}$ goes from $t_+$ to $t'$ and $\bfk''$ goes from $t'$ to $t''$.
        Then $\eta^{\widetilde B^{t_+}}_\bfk = \eta^{\widetilde B^{t'}}_{\bfk''}\eta^{\widetilde B^{t_+}}_{\bfk'}$.
    \end{enumerate}
  \end{lemma}

  For $\lambda\in\RR^m$ and a sequence $\bfk=(k_N,\ldots,k_1)$ of mutations from $t_+$ to $t$, define 
  \[S_{\bfk,\lambda}:=\left\{\left(\eta^{\widetilde B^{t_+}}_\bfk\right)^{-1}\big(\eta^{\widetilde B^{t_+}}_\bfk(\lambda)+\widetilde B^t\alpha\big):\alpha\in\RR^n_{\ge0}\right\}.\]
  
  \begin{definition}
    For $\lambda\in\RR^m$, define the \emph{dominance region} 
    \[
      \cP_\lambda = \bigcap_\bfk S_{\bfk,\lambda}.
    \]
    When $\mu\in\cP_\lambda$, we say \emph{$\lambda$ dominates $\mu$}.
    Write $\cP_\lambda^\ZZ:=\cP_\lambda\cap \widetilde B^+ \cdot \ZZ_{\ge0}^n$. 
  \end{definition}

  \begin{theorem}
    \cite{qin}
    $\cP_\ZZ(\lambda)$ controls the deformations of a basis element pointed at $\widetilde\lambda$.
  \end{theorem}


  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \section{Weyl group combinatorics of mutations}
  Let $A^+=(a_{ij})$ denote the Cartan companion of $B^{t_+}$.
  Fix an $n$-dimensional vector space $V$ with basis $\alpha^\vee_1,\ldots,\alpha^\vee_n$, called the \emph{simple coroots}.
  Define \emph{simple roots} $\alpha_i:=d_i\alpha^\vee_i$ which provide another basis of $V$.
  We will use the bilinear pairing $K$ on $V$ defined by $K(\alpha^\vee_i,\alpha_j)=a_{ij}$.
  This defines the \emph{simple reflections} $s_i(\beta)=\beta-K(\alpha^\vee_i,\beta)\alpha_i$ and the corresponding Weyl group $W=\langle s_1,\ldots,s_n\rangle$ acting linearly on $V$.
  Write $S=\{s_1,\ldots,s_n\}$ for the collection of simple reflections.
  Given $I\subseteq S$, let $W_I=\langle s:s\in I\rangle$ denote the \emph{parabolic subgroup} generated by $I$.
  For $s\in S$, write $[s]=S\setminus\{s\}$.

  Let $c=s_1\cdots s_n$ be the \emph{Coxeter element} of $W$ associated to $B^{t_+}$.
  More generally, any element of $W$ that can be obtained as the product of all elements of $S$ in some order is a \emph{Coxeter element}.
  An element $s\in S$ is \emph{initial} in $c$ if $\ell(sc)<\ell(c)$, in this case $sc$ is a Coxeter element of $W_{[s]}$.
  When $s_k$ is initial in $c$, $s_k c s_k$ is the Coxeter element associated to $\mu_k B^{t_+}$.
  An element $w\in W$ is \emph{$c$-sortable} if the following recursive definition holds
  \begin{itemize}
    \item the identity element of $W$ is $c$-sortable;
    \item if $s$ is initial in $c$ and $\ell(sw)<\ell(w)$, then $w$ is $c$-sortable if and only if $sw$ is $scs$-sortable;
    \item if $s$ is initial in $c$ and $\ell(sw)>\ell(w)$, then $w$ is $c$-sortable if and only if $w\in W_{[s]}$ is $sc$-sortable.
  \end{itemize}

  Statement about constructing $C(v)$ from skips.

  
  







  \begin{definition}
    We say $\nu,\lambda\in\RR^m$ are in the same \emph{$\widetilde B^+$-class} if they lie in the same domain of linearity for $\eta^{\widetilde B^+}_\bfk$ for all sequences $\bfk$.
    Define the \emph{mutation fan} $\cF_{\widetilde B^+}$ whose maximal cones are the closures of the $\widetilde B^+$-classes.
  \end{definition}
  \begin{remark}
    $\cF_{\widetilde B^+}=\cF_{B^+}\times \RR^{m-n}$ since the linearity domain in which $\nu$ lies depends only on its first $n$ coordinates.
  \end{remark}

  Cite these results for affine types:
  \begin{itemize}
    \item $\cF_{B^+}$ is simplicial and complete 
    \item $\cF_{B^+}$ is equivalent to the (transposed) scattering diagram fan and the associahedron(?) fan
    \item A maximal (by inclusion) cone $K$ in $\cF_{B^+}$ is \emph{real} if there exists $t\in\TT_n$ such that $K=K_t:=G^t\cdot\RR^n_{\ge0}$, otherwise it is \emph{imaginary}.
    \item There is a finite of imaginary cones.
    \item Any maximal imaginary cone $K$ is $n-1$ dimensional and is contained in $\delta^\perp$ (need to define $\delta$ and $\perp$)
    \item There exists $N>0$ so that $c^N$ (as it acts on weights) fixes $K$ pointwise
    \item $-\frac12 B^+\cdot\delta$ is one of the primitive vectors spanning a ray of $K$
    \item Let $\eta_1,\ldots,\eta_{n-2}$ be the other $n-2$ primitive vectors spanning rays of $K$.  
    \item Then there exists a real cone $H$ in $\cF_{B^+}$ such that
      \begin{itemize}
        \item $\eta_1,\ldots,\eta^{n-2}$ span rays of $H$
        \item $c^{\ell N} H$ is a real cone for all $\ell\ge0$
        \item $\lim\limits_{\ell\to\infty} c^{\ell N} H = K$
      \end{itemize}
      The second condition above defines a sequence $t_\ell\in\TT_n$ that \emph{converges} to $K$.
    \item Let $\eta_{n-1},\eta_n$ be the remaining primitive vectors spanning rays of $H$.  Then, in the appropriate scaling limit, both of these vectors limit to $-\frac12 B^+\cdot\delta$ under the action of $c^{\ell N}$ as $\ell\to\infty$.
  \end{itemize}

  Part of $\cF_{B^+}$ is the Cambrian fan
  
  after Prop. 5.4 in \cite{combinatorial_frameworks} gives C-matrices explicitly

  \begin{theorem}
    Let $\widetilde\lambda$ be imaginary with $s$ minimal such that $\widetilde\lambda+s\widetilde B^+\cdot\delta$ is real.
    \saySS{We need to say why such an $s$ exists.}
    Then the dominance region $\cP(\widetilde\lambda)$ is the segment $\{\widetilde\lambda+r\widetilde B^+\cdot\delta:0\le r\le s\}$.
  \end{theorem}
  \begin{remark}
    When $\widetilde B^+$ is full rank, $\cP_\ZZ(\widetilde\lambda)$ contains points of the form $\widetilde\lambda+r\widetilde B^+\cdot\delta$ with $r\in\ZZ_{\ge0}$.
    Without the full rank assumption, this no longer has to hold.
  \end{remark}
  \begin{proof}
  $ $
    \begin{itemize}
      \item[\checkmark] $\cP(\widetilde\lambda)$ is contained in the imaginary cone.
        $\cP(\widetilde\lambda)$ is contained in $\widetilde\lambda + \widetilde B^+ \cdot \RR_{\ge0}^n$ which is a proper cone since $\widetilde B^+$ is full rank.
        In particular, for sufficiently large $r$, $\cP(\widetilde\lambda)$ doesn't contain $-r \widetilde B^+\cdot \delta$.
        Then for any point $\widetilde\mu$ outside the closure of the imaginary cone, for sufficiently large $\ell$ the vector $c^\ell \widetilde\mu$ has large magnitude and is arbitrarily close the imaginary ray.
      \item $\cP(\widetilde\lambda)$ is contained in the ray $\{\widetilde\lambda+r\widetilde B^+\cdot\delta:r\ge 0\}$.
        \begin{itemize}
          \item Define green and red regions for real $\widetilde\lambda$.
          \item Compute the green and red regions as $\widetilde\lambda \pm \widetilde B^+\cdot C^t\cdot \RR_{\ge0}^n$.
            Use $\widetilde G^t\widetilde B^t = \widetilde B^+ C^t$.
          \item Limits of regions make sense because of continuity after intersecting with domains of linearity.
          \item Use limits of $C^t$ to draw the conclusion.
        \end{itemize}
      \item[\checkmark] $\cP(\widetilde\lambda)$ contains $\{\widetilde\lambda+r\widetilde B^+\cdot\delta:0\le r\le s\}$.
        \begin{itemize}
          \item $\delta$ spans the kernel of the Cartan companion $A$ of $B^+$ as well as any number of Coxeter mutations away
          \item after sufficiently many Coxeter mutations, the seed $t$ lies entirely on one side of the imaginary hyperplane and so the kernel $\kappa_t$ of the quasi-Cartan companion is sign coherent

            \emph{proof}: Since $A^t:=(C^{\vee,t})^T A_0 C^t$ then $G^t A^t (G^{\vee,t})^T:=A_0$. Since $G^t $ is invertible $A_0\cdot \delta = 0$ implies $A^t (G^{\vee,t})^T \cdot \delta = 0$ i.e. $(G^{\vee,t})^T \cdot \delta$ spans the kernel of $A^t$. After sufficiently many coxeter all the g-vectors at $t$ are on the positive side of $\delta^\perp$ and the result follows.
          \item for $t'$ connected to $t$ by mutation in direction $k$, we want $\eta_k^{\widetilde B^t}(\widetilde B^t\cdot\kappa_t)=\widetilde B^{t'}\cdot\kappa_{t'}$
          \item $\eta_k^{\widetilde B^t}(\widetilde B^t\cdot\kappa_t)=\widetilde E^t_{k,\varepsilon}\widetilde B^t\cdot\kappa_t=\widetilde E^t_{k,\varepsilon}\widetilde B^t F^t_{k,\varepsilon} F^t_{k,\varepsilon}\cdot\kappa_t = \widetilde B^{t'} \cdot F^t_{k,\varepsilon} \kappa_t $ but $\kappa_{t'}= F^t_{k,\varepsilon_{trop}} \kappa_t$
          \item For Cambrian mutations, $\varepsilon_{trop}$ is always positive.
            This follows from the explicit formula for $\bfc$-vectors in \cite{cambrian_frameworks} after Prop. 5.4.
          \item The $k$-th row of $F^t_{k,+}+F^t_{k,-}$ is the negative of the $k$-th row of the associated Cartan companion (not quasi)
          \item The $k$-th row of $F^t_{k,-}-F^t_{k,+}$ is the $k$-th row of $\widetilde B^t$
          \item The $k$-th entries of $\widetilde B^{t'} \cdot F^t_{k,\varepsilon} \kappa_t$ and $\widetilde B^{t'} \cdot \kappa_{t'}$ are the same
          \item $A^t:=(C^{\vee,t})^T A_0 C^t$
          \item $A^{t'}=(F^{t,\vee}_{k,\varepsilon_{trop}})^T A_t F^t_{k,\varepsilon_{trop}}$
        \end{itemize}
      \item For (sufficiently) Cambrian seeds $t$, the sign of the $k$-th entry of $\widetilde B^t (G^{\vee,t})^T \delta$ is the same as the sign of the $k$-th $\bfc$-vector since $\widetilde B^t (G^{\vee,t})^T \delta=(C^{\vee,t})^T B^+ \delta = -2 (C^{\vee,t})^T \nu_c(\delta)$ and $\nu_c$ is given by the negative of the Euler matrix.
    \end{itemize}

  \end{proof}

  %%%%%%%%%%%%%%%%%%%%%%%%
  \section{$\bfc$-vectors and $\bfg$-vectors}

  Definition $\bfc$-matrices $C^t$, for $t\in\TT_n$, recursively as follows:
  \begin{itemize}
    \item $C^{t_+} = \bOne_n$ is the $n\times n$ identity matrix;
    \item when $t$ and $t'$ are joined by an edge labeled $k$, $C^{t'}=(c^{t'}_{ij})$ is related to $C^t=(c^t_{ij})$ by
      \begin{equation}
        \label{eq:c-matrix mutation}
        c^{t'}_{ij} = \begin{cases} -c^t_{ij} & \text{if $i=k$ or $j=k$;}\\ c^t_{ij} + [-\varepsilon c^t_{ik}]_+ b^t_{kj} + c^t_{ik} [\varepsilon b^t_{kj}]_+ & \text{otherwise;} \end{cases}
      \end{equation}
      for any choice of sign $\varepsilon\in\{\pm1\}$.
  \end{itemize}

  Following \cite{keller,ghkk} it is known that the column of $C^t$ are always \emph{sign-coherent}, i.e. all entries of each column $C^t_{\bullet k}$ are either all nonnegative or all nonpositive.
  Write $\varepsilon^t_k$ for the sign of the nonzero entries of the $k$-th column of $C^t$.
  Using this choice of sign, the expression in \eqref{eq:c-matrix mutation} simplifies to
  \begin{equation}
    \label{eq:reduced c-matrix mutation}
    c^{t'}_{ij} = \begin{cases} -c^t_{ij} & \text{if $i=k$ or $j=k$;}\\ c^t_{ij} + c^t_{ik} [\varepsilon^t_k b^t_{kj}]_+ & \text{otherwise.} \end{cases}
  \end{equation}

  \begin{lemma}
    \label{le:c-matrix factorization}
    Suppose $t$ is obtained from $t_+$ by mutating along the sequence $\bfk=(k_N,\ldots,k_1)$ passing through $t_+=t_1,\ldots,t_N,t_{N+1}=t$.
    Then $C^t$ can be factored as $F^{t_1}_{k_1,-\varepsilon^{t_1}_{k_1}}\cdots F^{t_N}_{k_N,-\varepsilon^{t_N}_{k_N}}$.
  \end{lemma}
  \begin{proof}
    The recursion \eqref{eq:reduced c-matrix mutation} can be rewritten as $C^{t'}=C^t F^t_{k,-\varepsilon^t_k}$ and the claim follows by induction.
  \end{proof}

  Define $\bfg$-matrices $\widetilde G^t$, for $t\in\TT_n$, recursively as follows:
  \begin{itemize}
    \item $\widetilde G^{t_+} = \bOne_m$ is the $m\times m$ identity matrix;
    \item when $t$ and $t'$ are joined by an edge labeled $k$, $\widetilde G^{t'}=(g^{t'}_{ij})$ is related to $\widetilde G^t=(g^t_{ij})$ by
      \begin{equation}
        \label{eq:g-matrix mutation}
        g^{t'}_{ij} = \begin{cases} -g^t_{ik} + \sum\limits_{\ell=1}^m g^t_{i\ell} [-b^t_{\ell k} \varepsilon^t_k]_+ & \text{if $j=k$;}\\ g^t_{ij} & \text{otherwise.} \end{cases}
      \end{equation}
  \end{itemize}
  Note that the $\bfg$-matrices can also be defined via an arbitrary sign $\varepsilon\in\{\pm 1\}$ as in \eqref{eq:c-matrix mutation}, however such a general expression is unnecessary for our purposes.
  \begin{remark}
    Since we only mutate in directions $k\in[1,n]$, $\widetilde G^t$ has the following block form:
    \[\left[\begin{array}{cc} G^t & 0\\ * & \bOne_{m-n}\end{array}\right]\]
    where $G^t$ is the $n\times n$ $\bfg$-matrix for the coefficient-free case.
  \end{remark}

  \begin{lemma}
    \label{le:g-matrix factorization}
    Suppose $t$ is obtained from $t_+$ by mutating along the sequence $\bfk=(k_N,\ldots,k_1)$ passing through $t_+=t_1,\ldots,t_N,t_{N+1}=t$.
    Then $\widetilde G^t$ can be factored as $\widetilde E^{t_1}_{k_1,-\varepsilon^{t_1}_{k_1}}\cdots \widetilde E^{t_N}_{k_N,-\varepsilon^{t_N}_{k_N}}$.
  \end{lemma}
  \begin{proof}
    The recursion \eqref{eq:g-matrix mutation} can be rewritten as $\widetilde G^{t'}=\widetilde G^t \widetilde E^t_{k,-\varepsilon^t_k}$ and the claim follows by induction.
  \end{proof}
  \begin{proof}
    This is immediate from the definition \eqref{eq:g-matrix mutation}.
  \end{proof}

  \begin{corollary}
    \label{cor:GB=BC}
    For any $t\in\TT_n$, we have
    \[\widetilde G^t\widetilde B^t=\widetilde B^+ C^t.\]
  \end{corollary}
  \begin{proof}
    Suppose $t$ is obtained from $t_+$ by mutating along the sequence $\bfk=(k_N,\ldots,k_1)$ passing through $t_+=t_1,\ldots,t_N,t_{N+1}=t$.
    Then, by definition, we have
    \[ \widetilde B^t = \mu_\bfk \widetilde B^+ = \widetilde E^{t_N}_{k_N,-\varepsilon^{t_N}_{k_N}}\cdots \widetilde E^{t_1}_{k_1,-\varepsilon^{t_1}_{k_1}} \widetilde B^+ F^{t_1}_{k_1,-\varepsilon^{t_1}_{k_1}}\cdots F^{t_N}_{k_N,-\varepsilon^{t_N}_{k_N}}, \]
    and the result follows from Lemma~\ref{le:c-matrix factorization} and Lemma~\ref{le:g-matrix factorization} using the identity $(E^t_{k,\varepsilon})^2=\bOne_m$.
  \end{proof}

  It will be convenient to introduce $m\times m$ matrices $\widetilde C^{\vee,t}$ and $n\times n$ matrices $G^{\vee,t}$ for $t\in\TT_n$ defined recursively by $\widetilde C^{\vee,t_+}=\bOne_m$, $G^{\vee,t_+}=\bOne_n$, and 
  \begin{align}
    \label{eq:dual c-matrix mutation}
    c^{\vee,t'}_{ij} &= \begin{cases} -c^{\vee,t}_{ij} & \text{if $i=k$ or $j=k$;}\\ c^{\vee,t}_{ij} + c^{\vee,t}_{ik} [-b^t_{jk} \varepsilon^t_k]_+ & \text{otherwise;} \end{cases}\\
    \label{eq:dual g-matrix mutation}
    g^{\vee,t'}_{ij} &= \begin{cases} -g^{\vee,t}_{ik} + \sum\limits_{\ell=1}^n g^{\vee,t}_{i \ell} [\varepsilon^t_k b^t_{k \ell}]_+ & \text{if $j=k$;}\\ g^{\vee,t}_{ij} & \text{otherwise;} \end{cases}
  \end{align}
  whenever $\widetilde C^{\vee,t}=(c^{\vee,t}_{ij})$ (resp. $G^{\vee,t}=(g^{\vee,t}_{ij})$) is related to $\widetilde C^{\vee,t'}=(c^{\vee,t'}_{ij})$ (resp. $G^{\vee,t'}=(g^{\vee,t'}_{ij})$) by mutation in direction $k$.
  \begin{remark}
    \label{rem:dual c-matrix structure}
    Since we only mutate in directions $k\in[1,n]$, $\widetilde C^{\vee,t}$ has the following block form:
    \[\left[\begin{array}{cc} C^{\vee,t} & *\\ 0 & \bOne_{m-n}\end{array}\right]\]
    where $C^{\vee,t}$ is the $n\times n$ $\bfc$-matrix for $-B^T$.
  \end{remark}
  \begin{lemma}
    \label{le:tropical signs}
    For $1\le k,\ell\le n$, we have $d_k c^t_{k\ell} = c^{\vee,t}_{k\ell} d_\ell $ and $d_k g^t_{k\ell} = g^{\vee,t}_{k\ell} d_\ell$.
    In particular, $D C^t = C^{\vee,t} D$ and so the first $n$ columns of $\widetilde C^{\vee,t}$ share the same tropical signs with the $n$ columns of $C^t$.
  \end{lemma}
  \begin{proof}
    The first claim is an easy induction using \eqref{eq:reduced c-matrix mutation} and \eqref{eq:dual c-matrix mutation} or \eqref{eq:g-matrix mutation} and \eqref{eq:dual g-matrix mutation} together with the identity $d_k b^t_{k\ell} = - d_\ell b^t_{\ell k}$.
    The second claim is an immediate consequence.
  \end{proof}

  \begin{lemma}
    \label{le:factorize dual matrices}
    Suppose $t$ is obtained from $t_+$ by mutating along the sequence $\bfk=(k_N,\ldots,k_1)$ passing through $t_+=t_1,\ldots,t_N,t_{N+1}=t$.
    Then the following hold.
    \begin{enumerate}
      \item $\widetilde C^{\vee,t}$ can be factored as $\big(\widetilde E^{t_1}_{k_1,-\varepsilon^{t_1}_{k_1}}\big)^T \cdots \big(\widetilde E^{t_N}_{k_N,-\varepsilon^{t_N}_{k_N}}\big)^T$.
        In particular, $\big(\widetilde C^{\vee,t}\big)^T=\big(\widetilde G^t\big)^{-1}$.
      \item $G^{\vee,t}$ can be factored as $\big(F^{t_1}_{k_1,-\varepsilon^{t_1}_{k_1}}\big)^T \cdots \big(F^{t_N}_{k_N,-\varepsilon^{t_N}_{k_N}}\big)^T$.
        In particular, $\big(G^{\vee,t}\big)^T=\big(C^t\big)^{-1}$.
    \end{enumerate}
  \end{lemma}
  \begin{proof}
    The recursions \eqref{eq:dual c-matrix mutation} and \eqref{eq:dual g-matrix mutation} can be written as $\widetilde C^{\vee,t'}=\widetilde C^{\vee,t} \big(\widetilde E^t_{k,-\varepsilon^t_k}\big)^T$ and $G^{\vee,t'}=G^{\vee,t} \big(F^t_{k,-\varepsilon^t_k}\big)^T$ respectively.
    The first claims then follow by induction.
    The second claims follow from the identities $\big(\widetilde E^t_{k,-\varepsilon^t_k}\big)^2=\bOne_m$ and $\big(F^t_{k,-\varepsilon^t_k}\big)^2=\bOne_n$.
  \end{proof}

  \begin{corollary}
    \label{cor:dual BG=CB}
    For any $t\in\TT_n$, we have
    \[\widetilde B^t \big(G^{\vee,t}\big)^T=\big(\widetilde C^{\vee,t}\big)^T \widetilde B^+.\]
  \end{corollary}

  The following is a well-known result from representation theory of associative algebras concerning the Euler paring that we recast here to save on notation; see \cite{dlab_ringel?} for the details.
  \begin{remark}
    Say something about quasi-Cartan companions.
  \end{remark}

  There exists a rank 2 cluster algebra with frozen variables $\eta_i$, with $\bfg$-vectors $\bfg_k$ for $k\in\ZZ$.
  This gives real clusters $X_k:=\{\eta_1,\ldots,\eta_{n-2},\bfg_k,\bfg_{k+1}\}$ such that $\lim_{j\to\infty} c^{j\ell}\bfg_k=\nu_c(\delta)$.

  \begin{lemma}
    There exist $\lambda_k\in\Span_{\ge0} X_k$ so that $\lim_{k\to\infty} \lambda_k=\lambda$.
  \end{lemma}


  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \section{Green and Red Regions}

  \begin{definition}
    Consider real $\widetilde \lambda$, say $\widetilde \lambda\in \widetilde K_t:= K_t\times \RR^{m-n}$.
    Let $t$ be connected to $t_+$ by a sequence of edges labeled by $\bfk^+=(k_N,\ldots k_1)$. 
    Define the \emph{green cone} $S_\lambda^+:=S_{\bfk^+,\widetilde\lambda}\cap\widetilde K_t$.
    Similarly, let $\bfk^-=(n,\ldots,1,k_N,\ldots,k_1)$ and define the \emph{red cone} $S_\lambda^-:=S_{\bfk^-,\widetilde\lambda}\cap\widetilde K_t$.
  \end{definition}

  Define $S^\pm_\lambda:=\lim_{k\to\infty} S^\pm_{\lambda_k}$.

  \begin{lemma}
    $\cP(\lambda) \subseteq \Lambda^\pm_\lambda$
  \end{lemma}

  \begin{lemma}
    Consider $\lambda$ inside the $\bfg$-vector fan, say $\lambda$ lies inside the cone spanned by $G_t$.
    Then the intersection of $\phi_t^{-1} \cC_t(\phi_t \lambda)$ with this $\bfg$-cone is spanned by the columns of $\widetilde B^+ C^t$.
  \end{lemma}

  \begin{lemma}
    Similar statement for the red region
  \end{lemma}

  \begin{corollary}
    Let $\lambda\in\ZZ^m$ correspond to a cluster monomial
    \sayDR{Possibly multiplied by a Laurent monomial in coefficients}. 
    Then $\cP(\lambda)=\{\lambda\}$.
  \end{corollary}
  \begin{remark}
    This uses full rank assumption.
  \end{remark}

  \begin{lemma}
    For imaginary $\lambda$, $\Lambda^+_\lambda\cap\Lambda^-_\lambda$ is the line through $\lambda$ in direction $\nu_c(\delta)$.
  \end{lemma}

  \begin{corollary}
    Assume $\widetilde B$ is affine.
    For imaginary $\lambda$, $\cP(\lambda)$ is contained in the line through $\lambda$ in direction $\nu_c(\delta)$. 
  \end{corollary}


  %%%%%%%%%%%%%%%%%%%%%
  \section{Affine Type}


  Let $B$ be an acyclic exchange matrix of affine type with $DB$ skew-symmetric.
  Write $A$ for the Cartan companion of $B$ and note that $A$ has corank 1.
  Consider $B^t$ mutation equivalent to $B$ and $C^t$ the associated $\bfc$-matrix.

  Let $A_0$ denote the Cartan companion of $B$ and write $\delta_0$ for the positive vector spanning the kernel of $A_0$.
  For $t\in\TT_n$, let $A^t:=(C^{\vee,t})^T A_0 C^t$ denote the Reading-Speyer quasi-Cartan companion of $B^t$ \cite[Cor. 3.29]{Combinatorial_frameworks_for_cluster_algebras}.
  \begin{theorem}
    Let $\delta^t$ be the absolute value of the kernel of $A^t$.
    Then the primitive purely imaginary $\bfg$-vector direction at the seed $t$ is $-B^t\delta^t/2$.
  \end{theorem}

  \begin{lemma}
    The matrix $\cE^t A^t \cE^t$ is an admissible quasi-Cartan companion of $B^t$ of corank 1.
    Moreover, the kernel of $A^t$ is spanned by a non-negative vector $\delta^t$. 
  \end{lemma}

  Define $\zeta^t := -B^t \delta^t$.
  \begin{lemma}
    The vector $\zeta^t$ is an imaginary $\bfg$-vector.
  \end{lemma}

  \begin{lemma}
    With respect to the seed $t$, the $\bfd$-vector of the imaginary theta basis element $\vartheta_{\zeta^t}$ is $\delta^t$. 
  \end{lemma}
  \sayDR{Is this worth keeping}


\bibliographystyle{amsalpha}
\bibliography{bibliography}  

\end{document}
